Identification of protoneutron star g-modes in gravitational-wave data

### 2020-08-12 simulations.tex

\maob{%%
  We apply our analysis to a set of 25 spherically symmetric
  \citep{Torres:2019} and 7 two-dimensional axisymmetric models of
  stellar core collapse simulated with two codes, CoCoNuT
  (one-dimensional models) and AENUS-ALCAR
  \citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}
  (one- and two-dimensional models).  CoCoNuT
  \citep{Cerda-Duran__2008__AA__GRMHD-code} is a code for general
  relativistic hydrodynamics coupled to the Fast Multigroup Transport
  scheme \citep{Mueller_Janka_2015_FMT} providing an approximate
  description of the emission and transport of neutrinos.  AENUS-ALCAR
  \citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}
  combines special relativistic (magneto-)hydrodynamics, a modified
  Newtonian gravitational potential approximating the effects of
  general relativity \citep{Marek_etal__2006__AA__TOV-potential}, and
  a spectral two-moment neutrino transport solver
  \citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}.
  We included the relevant reactions between matter and neutrinos of
  all flavours, i.e., emission and absorption by nucleons and nuclei,
  electron-positron pair annihilation, nucleonic bremsstrahlung, and
  scattering off nucleons, nuclei, and electrons.
  %%
}

\maob{%%
  Our spherically symmetric simulations cover the range of initial
  stellar masses $M_{\mathrm{ZAMS}} = 11.2 - 75 \, \Msol$.  They were
  carried out using six equations of state (EOSs).  They are
  complemented by a set of two-dimensional axisymmetric models
  consisting of stellar core collapse of five stars with zero-age
  main-sequence masses of $M_{\mathrm{ZAMS}} = 11.2 - 40 \, \Msol$
  evolved through the hydrostatic phases by
  \cite{Woosley_Heger_Weaver__2002__ReviewsofModernPhysics__The_evolution_and_explosion_of_massive_stars}.
  We performed one simulation of each stellar model using the equation
  of state of \cite{Lattimer_Swesty__1991__NuclearPhysicsA__LS-EOS}
  with an incompressibility of $K = 220 \, \mathrm{MeV}$ and added
  comparison models with the SFHo EOS
  \cite{Steiner_et_al__2013__apj__Core-collapseSupernovaEquationsofStateBasedonNeutronStarObservations}
  and the EOS of
  \cite{Shen_et_al__2011__prc__Newequationofstateforastrophysicalsimulations}
  for the one with $M_{\mathrm{ZAMS}} = 15 \, \Msol$ (see Table
  \ref{Tab:2dSimList} for a list of models).
  %%
}

>>>>

\maob{%%
  We apply our analysis to spherically symmetric
  \citep{Torres:2019} and two-dimensional axisymmetric models of
  stellar core collapse simulated with two codes, CoCoNuT
  (one-dimensional models) and AENUS-ALCAR
  \citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}
  (one- and two-dimensional models).  CoCoNuT
  \citep{Cerda-Duran__2008__AA__GRMHD-code} is a code for general
  relativistic hydrodynamics coupled to the Fast Multigroup Transport
  scheme \citep{Mueller_Janka_2015_FMT} providing an approximate
  description of the emission and transport of neutrinos.  AENUS-ALCAR
  \citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}
  combines special relativistic (magneto-)hydrodynamics, a modified
  Newtonian gravitational potential approximating the effects of
  general relativity \citep{Marek_etal__2006__AA__TOV-potential}, and
  a spectral two-moment neutrino transport solver
  \citep{Just_et_al__2015__mnras__Anewmultidimensionalenergy-dependenttwo-momenttransportcodeforneutrino-hydrodynamics}.
  We included the relevant reactions between matter and neutrinos of
  all flavours, i.e., emission and absorption by nucleons and nuclei,
  electron-positron pair annihilation, nucleonic bremsstrahlung, and
  scattering off nucleons, nuclei, and electrons.
  %%
}

\maob{%%
  We use two sets of 25 models in the range of initial stellar masses
  $M_{\mathrm{ZAMS}} = 11.2 - 75 \, \Msol$ simulated with the two
  codes.  They were carried out using six equations of state (EOSs).
  They are complemented by a set of 7 two-dimensional axisymmetric
  models consisting of stellar core collapse of five stars with
  zero-age main-sequence masses of
  $M_{\mathrm{ZAMS}} = 11.2 - 40 \, \Msol$ evolved through the
  hydrostatic phases by
  \cite{Woosley_Heger_Weaver__2002__ReviewsofModernPhysics__The_evolution_and_explosion_of_massive_stars}.
  We performed one simulation of each stellar model using the equation
  of state of \cite{Lattimer_Swesty__1991__NuclearPhysicsA__LS-EOS}
  with an incompressibility of $K = 220 \, \mathrm{MeV}$ and added
  comparison models with the SFHo EOS
  \cite{Steiner_et_al__2013__apj__Core-collapseSupernovaEquationsofStateBasedonNeutronStarObservations}
  and the EOS of
  \cite{Shen_et_al__2011__prc__Newequationofstateforastrophysicalsimulations}
  for the one with $M_{\mathrm{ZAMS}} = 15 \, \Msol$ (see Table
  \ref{Tab:2dSimList} for a list of models).
  %%
}
